Tables

### 2018-11-02 code/tables.rmd
Improvements to Table 1 and 3, correction of reference in Table 2

##Heterogeneity may increase with effect size
```{r effect-size-heterogeneity-table}
#library(kableExtra)
rooted_relabilities <- matrix(rep(c(.6, .7,.8), 3), ncol = 3)
rho <- c(0, .3, .5)
rel <- c("R = .6", "R = .7", "R = .8")

@@

diff_row <- data.frame(rel = "Standard deviation R", X1 = sd(rooted_relabilities$X1), X2 = sd(rooted_relabilities$X2), X3 = sd(rooted_relabilities$X3))

@@

het_demo %>% knitr::kable("latex", booktabs = T, col.names = c("Effect size", "Rho = 0", "Rho = .3", "Rho = .5"), digits = 2) %>% 
  kable_styling(position = "left") %>% 
  footnote(threeparttable = TRUE,
           general = "R = square root of the multiplied reliabilities. Rho = true effect size. Code to reproduce table: osf.io/kf6pt/") %>% 
  row_spec(3, hline_after = T)

@@

#Shortened version of APA reference
papers <- c('Klein, R. A., Ratliff, K. A., Vianello, M., Adams, R. B., Jr., Bahník, S., Bernstein, M. J., . . . Nosek, B. A. (2014). Investigating variation in replicability: A "many labs" replication project.', 
'Ebersole, C. R., Atherton, O. E., Belanger, A. L., Skulborstad, H. M., Allen, J. M., Banks, J. B., ... & Brown, E. R. (2016). Many Labs 3: Evaluating participant pool quality across the academic semester via replication.',
'Ebersole, C. R., Atherton, O. E., Belanger, A. L., Skulborstad, H. M., Allen, J. M., Banks, J. B., ... & Brown, E. R. (2016). Many Labs 3: Evaluating participant pool quality across the academic semester via replication.',
'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahník, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990).',
'Eerland, A., Sherrill, A. M., Magliano, J. P., Zwaan, R. A., Arnal, J. D., Aucoin, P., ... & Crocker, C. (2016). Registered replication report: Hart & Albarracín (2011).',
'Hagger, M. S., Chatzisarantis, N. L., Alberts, H., Anggono, C. O., Batailler, C., Birt, A. R., ... & Calvillo, D. P. (2016). A multilab preregistered replication of the ego-depletion effect.',
'Cheung, I., Campbell, L., LeBel, E. P., Ackerman, R. A., Aykutoglu, B., Bahník, S., ... & Carcedo, R. J. (2016). Registered Replication Report: Study 1 from Finkel, Rusbult, Kumashiro, & Hannon (2002).',
'Wagenmakers, E. J., Beek, T., Dijkhoff, L., Gronau, Q. F., Acosta, A., Adams Jr, R. B., ... & Bulnes, L. C. (2016). Registered Replication Report: Strack, Martin, & Stepper (1988).',
'Bouwmeester, S., Verkoeijen, P. P., Aczel, B., Barbosa, F., Bègue, L., Brañas-Garza, P., ... & Evans, A. M. (2017). Registered Replication Report: Rand, Greene, and Nowak (2012).',
"O'Donnell, M., Nelson, L., McLatchie, N. M., & Lynott, D. J. (2017). Registered Replication Report: Dijksterhuis & van Knippenberg (1998)")

##Full APA reference below
# c('Klein, R. A., Ratliff, K. A., Vianello, M., Adams, R. B., Jr., Bahník, S., Bernstein, M. J., . . . Nosek, B. A. (2014). Investigating variation in replicability: A "many labs" replication project. Social Psychology, 45(3), 142-152.', 
# 'Ebersole, C. R., Atherton, O. E., Belanger, A. L., Skulborstad, H. M., Allen, J. M., Banks, J. B., ... & Brown, E. R. (2016). Many Labs 3: Evaluating participant pool quality across the academic semester via replication. Journal of Experimental Social Psychology, 67, 68-82.',
# 'Ebersole, C. R., Atherton, O. E., Belanger, A. L., Skulborstad, H. M., Allen, J. M., Banks, J. B., ... & Brown, E. R. (2016). Many Labs 3: Evaluating participant pool quality across the academic semester via replication. Journal of Experimental Social Psychology, 67, 68-82.',
# 'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahník, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990). Perspectives on Psychological Science, 9(5), 556-578.',
# 'Eerland, A., Sherrill, A. M., Magliano, J. P., Zwaan, R. A., Arnal, J. D., Aucoin, P., ... & Crocker, C. (2016). Registered replication report: Hart & Albarracín (2011). Perspectives on Psychological Science, 11(1), 158-171.',
# 'Hagger, M. S., Chatzisarantis, N. L., Alberts, H., Anggono, C. O., Batailler, C., Birt, A. R., ... & Calvillo, D. P. (2016). A multilab preregistered replication of the ego-depletion effect. Perspectives on Psychological Science, 11(4), 546-573.',
# 'Cheung, I., Campbell, L., LeBel, E. P., Ackerman, R. A., Aykutoglu, B., Bahník, S., ... & Carcedo, R. J. (2016). Registered Replication Report: Study 1 from Finkel, Rusbult, Kumashiro, & Hannon (2002). Perspectives on Psychological Science, 11(5), 750-764.',
# 'Wagenmakers, E. J., Beek, T., Dijkhoff, L., Gronau, Q. F., Acosta, A., Adams Jr, R. B., ... & Bulnes, L. C. (2016). Registered Replication Report: Strack, Martin, & Stepper (1988). Perspectives on Psychological Science, 11(6), 917-928.',
# 'Bouwmeester, S., Verkoeijen, P. P., Aczel, B., Barbosa, F., Bègue, L., Brañas-Garza, P., ... & Evans, A. M. (2017). Registered Replication Report: Rand, Greene, and Nowak (2012). Perspectives on Psychological Science, 12(3), 527-542.',
# "O'Donnell, M., Nelson, L., McLatchie, N. M., & Lynott, D. J. (2017). Registered Replication Report: Dijksterhuis & van Knippenberg (1998): Multilab direct replication of: A variant of study 4 from Dijksterhuis, A., & van Knippenberg, A.(1998). The relation between perception and behavior, or how to win a game of trivial pursuit. Journal of personality and social psychology. Perspectives on Psychological Science."

@@

#Combine dataframes to create full table
het <-  het %>% 
  left_join(I2_ci_lb) %>% 
  select(rp, effect,k , everything()) %>% 
  arrange(desc(s_I2),  desc(s_ci.ub)) #sort by I2 and upper CI bound

@@

het %>% knitr::kable("latex", align = "c", booktabs = TRUE,  digits = 2, col.names = c("RP", "Effect", "k", "Effect type", "Estimate", "I2(%)", "ci.lb", "ci.ub", "Zero", "Small", "Medium", "Large")) %>% 
  add_header_above(c(" " = 8, "Heterogeneity & error/power" = 4)) %>% 
  kable_styling("scale_down", font_size = 7) %>%
  footnote(threeparttable = TRUE, escape = FALSE,
           general = "Effects were estimated in metafor using REML. The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales'. RP = Replication Project, k = no. primary studies, Estimate = Point estimates of effect sizes, ci.lb = lower bound of $I^2$ 95\\\\% confidence interval, ci.ub = upper bound of $I^2$ 95\\\\% confidence interval. SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation. Code to reproduce table: osf.io/kf6pt/",
           alphabet = "These effects were simulated as standardized mean differences")

>>>>

##Heterogeneity may increase with effect size
```{r effect-size-heterogeneity-table}
#library(kableExtra)
rooted_relabilities <- matrix(rep(c(.6, .7,.8), 3), ncol = 3)
rho <- c(0, .3, .5)
rel <- c("$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8")

@@

diff_row <- data.frame(rel = "SD observed effect sizes", X1 = sd(rooted_relabilities$X1), X2 = sd(rooted_relabilities$X2), X3 = sd(rooted_relabilities$X3))

@@

het_demo %>% knitr::kable("latex", booktabs = T, col.names = c("", "$\\rho$ = 0", "$\\rho$ = .3", "$\\rho$ = .5"), escape = FALSE, digits = 2) %>% 
  kable_styling(position = "left") %>% 
  footnote(threeparttable = TRUE, escape = FALSE,
           general = "Values in cells are observed effect sizes arising from the true effect size $\\\\rho$ and measurement reliabilites $\\\\sqrt{R_{xx'}}\\\\times\\\\sqrt{R_{yy'}}$. SD = standard deviation. Code to reproduce table: osf.io/kf6pt/") %>% 
  row_spec(3, hline_after = T)

@@

#Shortened version of APA reference
papers <- c('Klein, R. A., Ratliff, K. A., Vianello, M., Adams, R. B., Jr., Bahník, S., Bernstein, M. J., . . . Nosek, B. A. (2014). Investigating variation in replicability: A "many labs" replication project.', 
'Ebersole, C. R., Atherton, O. E., Belanger, A. L., Skulborstad, H. M., Allen, J. M., Banks, J. B., ... & Brown, E. R. (2016). Many Labs 3: Evaluating participant pool quality across the academic semester via replication.',
'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahník, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990).',
'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahník, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990).',
'Eerland, A., Sherrill, A. M., Magliano, J. P., Zwaan, R. A., Arnal, J. D., Aucoin, P., ... & Crocker, C. (2016). Registered replication report: Hart & Albarracín (2011).',
'Hagger, M. S., Chatzisarantis, N. L., Alberts, H., Anggono, C. O., Batailler, C., Birt, A. R., ... & Calvillo, D. P. (2016). A multilab preregistered replication of the ego-depletion effect.',
'Cheung, I., Campbell, L., LeBel, E. P., Ackerman, R. A., Aykutoglu, B., Bahník, S., ... & Carcedo, R. J. (2016). Registered Replication Report: Study 1 from Finkel, Rusbult, Kumashiro, & Hannon (2002).',
'Wagenmakers, E. J., Beek, T., Dijkhoff, L., Gronau, Q. F., Acosta, A., Adams Jr, R. B., ... & Bulnes, L. C. (2016). Registered Replication Report: Strack, Martin, & Stepper (1988).',
'Bouwmeester, S., Verkoeijen, P. P., Aczel, B., Barbosa, F., Bègue, L., Brañas-Garza, P., ... & Evans, A. M. (2017). Registered Replication Report: Rand, Greene, and Nowak (2012).',
"O'Donnell, M., Nelson, L., McLatchie, N. M., & Lynott, D. J. (2017). Registered Replication Report: Dijksterhuis & van Knippenberg (1998)")

##Full APA reference below
# c('Klein, R. A., Ratliff, K. A., Vianello, M., Adams, R. B., Jr., Bahník, S., Bernstein, M. J., . . . Nosek, B. A. (2014). Investigating variation in replicability: A "many labs" replication project. Social Psychology, 45(3), 142-152.', 
# 'Ebersole, C. R., Atherton, O. E., Belanger, A. L., Skulborstad, H. M., Allen, J. M., Banks, J. B., ... & Brown, E. R. (2016). Many Labs 3: Evaluating participant pool quality across the academic semester via replication. Journal of Experimental Social Psychology, 67, 68-82.',
# 'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahník, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990). Perspectives on Psychological Science, 9(5), 556-578.',
# 'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahník, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990). Perspectives on Psychological Science, 9(5), 556-578.',
# 'Eerland, A., Sherrill, A. M., Magliano, J. P., Zwaan, R. A., Arnal, J. D., Aucoin, P., ... & Crocker, C. (2016). Registered replication report: Hart & Albarracín (2011). Perspectives on Psychological Science, 11(1), 158-171.',
# 'Hagger, M. S., Chatzisarantis, N. L., Alberts, H., Anggono, C. O., Batailler, C., Birt, A. R., ... & Calvillo, D. P. (2016). A multilab preregistered replication of the ego-depletion effect. Perspectives on Psychological Science, 11(4), 546-573.',
# 'Cheung, I., Campbell, L., LeBel, E. P., Ackerman, R. A., Aykutoglu, B., Bahník, S., ... & Carcedo, R. J. (2016). Registered Replication Report: Study 1 from Finkel, Rusbult, Kumashiro, & Hannon (2002). Perspectives on Psychological Science, 11(5), 750-764.',
# 'Wagenmakers, E. J., Beek, T., Dijkhoff, L., Gronau, Q. F., Acosta, A., Adams Jr, R. B., ... & Bulnes, L. C. (2016). Registered Replication Report: Strack, Martin, & Stepper (1988). Perspectives on Psychological Science, 11(6), 917-928.',
# 'Bouwmeester, S., Verkoeijen, P. P., Aczel, B., Barbosa, F., Bègue, L., Brañas-Garza, P., ... & Evans, A. M. (2017). Registered Replication Report: Rand, Greene, and Nowak (2012). Perspectives on Psychological Science, 12(3), 527-542.',
# "O'Donnell, M., Nelson, L., McLatchie, N. M., & Lynott, D. J. (2017). Registered Replication Report: Dijksterhuis & van Knippenberg (1998): Multilab direct replication of: A variant of study 4 from Dijksterhuis, A., & van Knippenberg, A.(1998). The relation between perception and behavior, or how to win a game of trivial pursuit. Journal of personality and social psychology. Perspectives on Psychological Science."

@@

#Combine dataframes to create full table
het <-  het %>% 
  left_join(I2_ci_lb) %>% 
  arrange(desc(s_I2),  desc(s_ci.ub)) %>% #sort by I2 and upper CI bound
  mutate(ci = paste0("[", trimws(format(round(s_ci.lb, 2), nsmall = 2)), ", ", trimws(format(round(s_ci.ub, 2), nsmall = 2)), "]")) %>% 
  select(rp, effect, k, effect_type, eff_size, s_I2, ci, zero, small, medium, large)

@@

het %>% knitr::kable("latex", align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "k", "Effect type", "Effect size estimate", "$I^2$(\\%)", "$I^2$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>% 
  add_header_above(c(" " = 7, "Level of heterogeneity" = 4)) %>% 
  add_header_above(c(" " = 7, "Statistical power" = 4)) %>% 
  kable_styling("scale_down", font_size = 7) %>%
  footnote(threeparttable = TRUE, escape = FALSE,
           general = "Effects were estimated in metafor using REML. The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales'. RP = Replication Project, k = no. primary studies, Estimate = Point estimates of effect sizes, $I^2$ 95\\\\% CI = $I^2$ 95\\\\% confidence interval. SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation. Code to reproduce table: osf.io/kf6pt/",
           alphabet = "These effects were simulated as standardized mean differences")
